### 2019-11-22 thesis.tex
after moving the solar physics appendix to introduction
* thesis.tex: Summary: before moving the solar physics appendix

The main subject of this thesis is discussed in \Cref{noneigenmode}. In
\Cref{sec:inc-non} we show the methodology used in the formulation of this
new generalization and the outcome of its inclusion in the quasilinear
wave equation, and in the particle kinetic equation. \Cref{sec:non-non}
describes the inclusion of the noneigenmode fluctuations in the nonlinear
wave equations and the resulting terms, which are the main concern of
the present analysis. In \Cref{main}, we contextualize the present work
regarding the theory discussed in the previous chapter and present the
results obtained in appended papers. \Cref{cha:final}, summarizes the
results and discuss some remarking conclusions obtained in this analysis.
At the end of this chapter, we also deliberate the perspectives for this
new generalized formalism and its relevance for the next generation of
solar physics research.
% LFZ190822: Suponho que aqui devia ser "... a brief discussion on the
% conclusions obtained and on the perspectives ..." ?
% Sabrina: Melhorou?
% and its relevance for the next generation of solar physics research are
% also deliberated.

In the end, we have five appendices. \Cref{appA} depicts an improved
approximation for the second order susceptibility of the electrostatic
bremsstrahlung for Langmuir waves. In \Cref{appB} we discuss the
similarities of the asymptotic equilibrium state of the Langmuir waves
spectrum, considering a combination of an inverse power-law kappa
distribution and a Maxwellian distribution, in the presence and the
absence of the electrostatic bremsstrahlung effect. The discussion in
\Cref{appB} is related with to article appended in \Cref{appC}, which
is parallel research and is only slightly related to the main subject
of this work. \Cref{master} shows the paper that summarizes the results
of my Master’s dissertation, which may be considered the starting point
of this doctoral research. \Cref{appE} explores relevant aspects of
current solar physics research and how they are connected to this work.
It was written to be more like a light, informative reading, than a
deep academic digression.

@@

\chapter{Applications to astrophysical plasmas}
\label{appE}
Astrophysical plasmas are observed in a vast range of densities, temperatures,
magnetic fields, ionization degree, and scale lengths\cite{peratt2014}. Starting
in the outer layers of Earth's atmosphere, passing through the solar wind in the
interplanetary space, to the stellar interiors and atmospheres, accretion disks
and molecular clouds, it is estimated that something around $99 \sim 99.9\%$ of the
observable matter in the universe is in the plasma state. Under cosmic conditions,
even the weakly ionized gas of the neutral hydrogen regions around galaxies or in
the atmosphere of cold stars have a strong reaction to electromagnetic fields,
exhibiting the characteristic collective behavior of plasmas and, therefore, are
also considered plasmas\cite{tsypa,may,peratt2014}.

\section{Solar and space physics}
\label{sec:solar-physics}
The domain of solar and space physics is the \emph{heliosphere}, a cavity
in the interstellar medium, created by the constant supersonic flow of solar
plasma that permeates the interplanetary space. This region encloses the
solar system and extends for approximately $140\unit{AU}$\footnote{An AU
  (astronomical unit) is defined as the mean distance between the Sun and
  Earth, $1\unit{AU}\approx 150\times 10^6\unit{km}$.} in the surrounding
galactic space. Its outer limit is the \emph{heliopause}, an interface
zone where the outgoing pressure of the solar plasma balances the incoming
pressure from the interstellar medium. This comet-shaped plasma bubble
\cite{Dialynas2017}, also has an inner boundary, the \emph{termination shock},
which delimits the sphere of absolute influence of the solar plasma. Beyond
the termination shock, at roughly $100\unit{AU}$ from the Sun, extending
out to the heliopause, lies the \emph{heliosheath}. In this region, the
solar wind particles start being subjected to increasing external pressure,
transitioning to a subsonic, turbulent flow that blends and interacts
directly with the matter in the local interstellar medium \cite{NAP13060}.
In \autoref{figE1}, we have a depiction of the regions and boundaries
described above, and the current location of both Voyager missions, that
are already outside the heliosphere, in the interstellar space.
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.892\textwidth]{solar_system_env.png}
    \caption{Main boundaries of the heliosphere and the location of both
      Voyager missions.}
      {\footnotesize Credit:}
      \href{https://voyager.jpl.nasa.gov/news/details.php?article_id=112}
      {\footnotesize NASA/JPL-Caltech}{\footnotesize , accessed at 08/08/2019.}
    \label{figE1}
  \end{center}
\end{figure}

>>>>

\section{Applications to astrophysical plasmas}
\label{appE}
Astrophysical plasmas are observed in a vast range of densities, temperatures,
magnetic fields, ionization degree, and scale lengths\cite{peratt2014}. Starting
in the outer layers of Earth's atmosphere, passing through the solar wind in the
interplanetary space, to the stellar interiors and atmospheres, accretion disks
and molecular clouds, it is estimated that something around $99 \sim 99.9\%$ of the
observable matter in the universe is in the plasma state. Under cosmic conditions,
even the weakly ionized gas of the neutral hydrogen regions around galaxies or in
the atmosphere of cold stars have a strong reaction to electromagnetic fields,
exhibiting the characteristic collective behavior of plasmas and, therefore, are
also considered plasmas\cite{tsypa,may,peratt2014}.

\subsection{Solar and space physics}
\label{sec:solar-physics}
The domain of solar and space physics is the \emph{heliosphere}, a cavity
in the interstellar medium, created by the constant supersonic flow of solar
plasma that permeates the interplanetary space. This region encloses the
solar system and extends for approximately $140\unit{AU}$\footnote{An AU
  (astronomical unit) is defined as the mean distance between the Sun and
  Earth, $1\unit{AU}\approx 150\times 10^6\unit{km}$.} in the surrounding
galactic space. Its outer limit is the \emph{heliopause}, an interface
zone where the outgoing pressure of the solar plasma balances the incoming
pressure from the interstellar medium. This comet-shaped plasma bubble
\cite{Dialynas2017}, also has an inner boundary, the \emph{termination shock},
which delimits the sphere of absolute influence of the solar plasma. Beyond
the termination shock, at roughly $100\unit{AU}$ from the Sun, extending
out to the heliopause, lies the \emph{heliosheath}. In this region, the
solar wind particles start being subjected to increasing external pressure,
transitioning to a subsonic, turbulent flow that blends and interacts
directly with the matter in the local interstellar medium \cite{NAP13060}.
In \autoref{figE1}, we have a depiction of the regions and boundaries
described above, and the current location of both Voyager missions, that
are already outside the heliosphere, in the interstellar space.
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.892\textwidth]{solar_system_env.png}
    \caption{Main boundaries of the heliosphere and the location of both
      Voyager missions.}
      {\footnotesize Credit:}
      \href{https://voyager.jpl.nasa.gov/news/details.php?article_id=112}
      {\footnotesize NASA/JPL-Caltech}{\footnotesize , accessed at 08/08/2019.}
    \label{figE1}
  \end{center}
\end{figure}

\section{Thesis organization}
\label{sec:thesis-organization}
The main subject of this thesis is discussed in \Cref{noneigenmode}. In
\Cref{sec:inc-non} we show the methodology used in the formulation of this
new generalization and the outcome of its inclusion in the quasilinear
wave equation, and in the particle kinetic equation. \Cref{sec:non-non}
describes the inclusion of the noneigenmode fluctuations in the nonlinear
wave equations and the resulting terms, which are the main concern of
the present analysis. In \Cref{main}, we contextualize the present work
regarding the theory discussed in the previous chapter and present the
results obtained in appended papers. \Cref{cha:final}, summarizes the
results and discuss some remarking conclusions obtained in this analysis.
At the end of this chapter, we also deliberate the perspectives for this
new generalized formalism and its relevance for the next generation of
solar physics research.
% LFZ190822: Suponho que aqui devia ser "... a brief discussion on the
% conclusions obtained and on the perspectives ..." ?
% Sabrina: Melhorou?
% and its relevance for the next generation of solar physics research are
% also deliberated.

In the end, we have four appendices. \Cref{appA} depicts an improved
approximation for the second order susceptibility of the electrostatic
bremsstrahlung for Langmuir waves. In \Cref{appB} we discuss the
similarities of the asymptotic equilibrium state of the Langmuir waves
spectrum, considering a combination of an inverse power-law kappa
distribution and a Maxwellian distribution, in the presence and the
absence of the electrostatic bremsstrahlung effect. The discussion in
\Cref{appB} is related with to article appended in \Cref{appC}, which
is parallel research and is only slightly related to the main subject
of this work. \Cref{master} shows the paper that summarizes the results
of my Master’s dissertation, which may be considered the starting point
of this doctoral research. % \Cref{appE} explores relevant aspects of
% current solar physics research and how they are connected to this work.
% It was written to be more like a light, informative reading, than a
% deep academic digression.

@@
